---
title: "Manipulate a Model by Selecting Data Points from the Iris Data Set"
author: "Maria Lauve"
date: "August 24, 2017"
runtime: shiny
output: ioslides_presentation
---

<style>
.title-slide {
    background-color: #deebf7
}
.title-slide hgroup > h1{
 color: #800000; 
}
slides > slide.title-slide p {
  color: #2c7fb8;
}
</style>

## Introduction to the Iris App

<style>
slide:not(.segue) h2{color: #800000}
slides > slide {
    background-color: #deebf7
</style>

<div class=blue3>
- The Iris app allows the user to experiment with manipulating a model that describes the relationship between the **Sepal Length** and **Petal Length** of Irises.
- The user can see how the relationship *changes* depending on the set of data points selected.
- The data points are color-coded by Species to allow the user to test whether the relationship between Sepal Length and Sepal Width changes depending on the species of the plant.
- The following slides contain an *interactive view of the app*, as well as *screenshots of the code* used to generate it.
</div>

## The Iris App

```{r, echo=FALSE}
library(shiny)

shinyApp(
  
 ui = fluidPage(
    titlePanel("Select Data Points to Visualize a Model"),
    sidebarLayout(
        sidebarPanel(
            h3("Slope"),
            textOutput("slopeOut"),
            h3("Intercept"),
            textOutput("intOut")
        ),
        mainPanel(
            plotOutput("plot1", brush = brushOpts(
                id = "brush1"
            ))
        )
    )
),

    server = function(input, output) {
    model <- reactive({
        brushed_data <- brushedPoints(iris, input$brush1,
                                      xvar = "Sepal.Length", yvar = "Petal.Length")
        if(nrow(brushed_data) < 2){
            return(NULL)
        }
        lm(Petal.Length ~ Sepal.Length, data = brushed_data)
    })
    
    output$slopeOut <- renderText({
        if(is.null(model())){
            "No Model Found"
        } else {
            model()[[1]][2]
        }
    })

        output$intOut <- renderText({
        if(is.null(model())){
            "No Model Found"
        } else {
            model()[[1]][1]
        }
    })
    
    output$plot1 <- renderPlot({
        plot(iris$Sepal.Length, iris$Petal.Length, xlab = "Sepal Length",
             ylab = "Petal Length", main = "Iris Measurements",
             cex = 1.5, pch = 16, bty = "n", col = factor(iris$Species))
        legend(list(x = 6.75, y = 3), c("Setosa", "Versicolor", "Verginica"),
               pch = 19, col=1:3)
            if(!is.null(model())){
            abline(model(), col = "blue", lwd = 2)
        }
    })
})

```

## ui.R code {.smaller}

```{r, eval=FALSE}
library(shiny)

shinyUI(fluidPage(
    titlePanel("Select Data Points to Visualize a Model"),
    sidebarLayout(
        sidebarPanel(
            h3("Slope"),
            textOutput("slopeOut"),
            h3("Intercept"),
            textOutput("intOut")
        ),
        mainPanel(
            plotOutput("plot1", brush = brushOpts(
                id = "brush1"
            ))
        )
    )
))
```

## server.R code {.smaller}

<style>
.slide {
    /*margin-top: -25px;
    margin-bottom: -25px*/
    padding: 5px 40px
}
</style>

```{r, eval=FALSE}
library(shiny)
shinyServer(function(input, output) {
    model <- reactive({
        brushed_data <- brushedPoints(iris, input$brush1,
                xvar = "Sepal.Length", yvar = "Petal.Length")
        if(nrow(brushed_data) < 2){return(NULL)}
        lm(Petal.Length ~ Sepal.Length, data = brushed_data)
    })
    output$slopeOut <- renderText({
        if(is.null(model())){"No Model Found"}
            else {model()[[1]][2]}
    })
        output$intOut <- renderText({
        if(is.null(model())){"No Model Found"}
            else {model()[[1]][1]}
    })
    output$plot1 <- renderPlot({
        plot(iris$Sepal.Length, iris$Petal.Length, xlab = "Sepal Length",
             ylab = "Petal Length", main = "Iris Measurements",
             cex = 1.5, pch = 16, bty = "n", col = factor(iris$Species))
        legend(list(x = 6.75, y = 3), c("Setosa", "Versicolor","Verginica"),
             pch = 19, col=1:3)
            if(!is.null(model())){abline(model(), col = "blue", lwd = 2)}
    })
})
```
        

```{r, echo=FALSE}
# RSconnect login:
# https://www.shinyapps.io/admin/#/login

# Run the following lines to post app to host server
#library(rsconnect)
#rsconnect::deployApp('./IrisApp')

# Shiny server URL for Shiny App
#https://mvl-coursera.shinyapps.io/irisapp/

# Github URL for presentation slides
#https://marialauve.github.io/Shiny-App-Assignment/IrisPresentation.html#1
    
```
