---
title: "Manipulate a Model by Selecting Data Points from the Iris Data Set"
author: "Maria Lauve"
date: "August 24, 2017"
output: ioslides_presentation
---

## Introduction to the Iris App

- The Iris app allows the user to experiment with manipulating a model that describes the relationship between the Sepal Length and Petal Length of Irises.
- The user can see how the relationship changes depending on the set of data points selected.
- The data points are color-coded by Species to allow the user to test whether the relationship between Sepal Length and Sepal Width changes depending on the species of the plant.
- The following slides contain an interactive view of the app, as well as screenshots of the code used to generate it.

## The Iris App

```{r, echo=FALSE}
library(shiny)

shinyApp(
  
 ui = fluidPage(
    titlePanel("Select Data Points to Visualize a Model"),
    sidebarLayout(
        sidebarPanel(
            h3("Slope"),
            textOutput("slopeOut"),
            h3("Intercept"),
            textOutput("intOut")
        ),
        mainPanel(
            plotOutput("plot1", brush = brushOpts(
                id = "brush1"
            ))
        )
    )
),

    server = function(input, output) {
    model <- reactive({
        brushed_data <- brushedPoints(iris, input$brush1,
                                      xvar = "Sepal.Length", yvar = "Petal.Length")
        if(nrow(brushed_data) < 2){
            return(NULL)
        }
        lm(Petal.Length ~ Sepal.Length, data = brushed_data)
    })
    
    output$slopeOut <- renderText({
        if(is.null(model())){
            "No Model Found"
        } else {
            model()[[1]][2]
        }
    })

        output$intOut <- renderText({
        if(is.null(model())){
            "No Model Found"
        } else {
            model()[[1]][1]
        }
    })
    
    output$plot1 <- renderPlot({
        plot(iris$Sepal.Length, iris$Petal.Length, xlab = "Sepal Length",
             ylab = "Petal Length", main = "Iris Measurements",
             cex = 1.5, pch = 16, bty = "n", col = factor(iris$Species))
        legend(list(x = 6.75, y = 3), c("Setosa", "Versicolor", "Verginica"),
               pch = 19, col=1:3)
            if(!is.null(model())){
            abline(model(), col = "blue", lwd = 2)
        }
    })
})

```

## ui.R code {.smaller}

```{r, eval=FALSE}
library(shiny)

shinyUI(fluidPage(
    titlePanel("Select Data Points to Visualize a Model"),
    sidebarLayout(
        sidebarPanel(
            h3("Slope"),
            textOutput("slopeOut"),
            h3("Intercept"),
            textOutput("intOut")
        ),
        mainPanel(
            plotOutput("plot1", brush = brushOpts(
                id = "brush1"
            ))
        )
    )
))
```


## server.R code (Part 1) {.smaller}

```{r, eval=FALSE}
library(shiny)
shinyServer(function(input, output) {
    model <- reactive({
        brushed_data <- brushedPoints(iris, input$brush1,
                                      xvar = "Sepal.Length", yvar = "Petal.Length")
        if(nrow(brushed_data) < 2){
            return(NULL)
        }
        lm(Petal.Length ~ Sepal.Length, data = brushed_data)
    })
    
    output$slopeOut <- renderText({
        if(is.null(model())){
            "No Model Found"
        } else {
            model()[[1]][2]
        }
    })
```
        
## server.R code (Part 2) {.smaller}

```{r, eval=FALSE}
    output$intOut <- renderText({
        if(is.null(model())){
            "No Model Found"
        } else {
            model()[[1]][1]
        }
    })
    
    output$plot1 <- renderPlot({
        plot(iris$Sepal.Length, iris$Petal.Length, xlab = "Sepal Length",
             ylab = "Petal Length", main = "Iris Measurements",
             cex = 1.5, pch = 16, bty = "n", col = factor(iris$Species))
        legend(list(x = 6.75, y = 3), c("Setosa", "Versicolor", "Verginica"), pch = 19, col=1:3)
            if(!is.null(model())){
            abline(model(), col = "blue", lwd = 2)
        }
    })
})
```

```{r, echo=FALSE}
# RSconnect login:
# https://www.shinyapps.io/admin/#/login

#library(rsconnect)
#rsconnect::deployApp('path/to/your/app')
```
